Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-04-08 chCS16/gully-santiago_m.tex
assign short figure captions to format nicely in the Table of Contents

\begin{figure}[!ht]
\plottwo{chCS16/gully-santiago_m_fig1}{chCS16/gully-santiago_m_fig2}
\caption{\emph{Left-} Spectral typing comparison for source 13 (derived SpT= M6), with spectral type comparison objects from the SpeX archive \citep{rayner09,cushing05}: Gl51 (M5V), and Gl644C (M7V).  \emph{Right-} Detail of the $\mathrm{Na\, I}$ line for source 13, with surface gravity comparison objects with identical spectral types, also from the SpeX archive: Gl406 (M6V) and HD196610 (M6 III).  Source 13 is intermediate in surface gravity as demonstrated by the gravity sensitive index $\mathrm{Na\, I}$.}
\end{figure}

\begin{figure}[!ht]
\plotone{chCS16/gully-santiago_m_fig3}
\caption{Gravity dependence of the $\mathrm{Na\, I}$ line.  Dwarfs and giants from the SpeX spectral atlas are shown as red diamonds and green triangles respectively.  The blue squares show the sources from this work.  Compare to figure 35 of \citet{rayner09}.}
\end{figure}

>>>>

\begin{figure}[!ht]
\plottwo{chCS16/gully-santiago_m_fig1}{chCS16/gully-santiago_m_fig2}
\caption[Spectral classification with spectral type standards and spectra of dwarfs and giants]{\emph{Left-} Spectral typing comparison for source 13 (derived SpT= M6), with spectral type comparison objects from the SpeX archive \citep{rayner09,cushing05}: Gl51 (M5V), and Gl644C (M7V).  \emph{Right-} Detail of the $\mathrm{Na\, I}$ line for source 13, with surface gravity comparison objects with identical spectral types, also from the SpeX archive: Gl406 (M6V) and HD196610 (M6 III).  Source 13 is intermediate in surface gravity as demonstrated by the gravity sensitive index $\mathrm{Na\, I}$.}
\end{figure}

\begin{figure}[!ht]
\plotone{chCS16/gully-santiago_m_fig3}
\caption[Gravity dependence of the $\mathrm{Na\, I}$ line]{Gravity dependence of the $\mathrm{Na\, I}$ line.  Dwarfs and giants from the SpeX spectral atlas are shown as red diamonds and green triangles respectively.  The blue squares show the sources from this work.  Compare to figure 35 of \citet{rayner09}.}
\end{figure}

### 2015-04-08 chSPIE_2012_CA1/chapter-2012-CA1.tex
assign short figure captions to format nicely in the Table of Contents

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{2010SPIE.7739E.146W}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=0.9\textwidth]{chSPIE_2012_CA1/figs/CA1a_fig_scl2}
  \caption{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b), with mirror 13a moved clear out of the beam path with a 90$^\circ$ flip mount.  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  There are typically 3 or 4 orders diffracted $\pm20^\circ$ from the optical axis, for CA1 in our wavelength range of interest ($1.5-2.5 \; \mu$m).  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The angular range of motion of the swing arm is about +27 to -37$^\circ$ which is set by limit switches and the rigid mechanical structure, which supports the immersion grating and its concomitant fine adjust positioning hardware.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The beam path in the monochromator is omitted for clarity.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}

>>>>

\begin{figure}
  \centering
  \subfloat[CA1a photo]{\label{fig:CA1aphoto}\includegraphics[height=5cm]{chSPIE_2012_CA1/figs/ca1_bartest2}}
	~
%  \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[page=1, trim=24cm 15.15cm 2cm 5cm, clip=true, totalheight=0.2\textheight ]{APRA_BOULE_29MM_R3_CA1_X14_2011-03-08}}
   \subfloat[CA1a drawing]{\label{fig:CA1adraw}\includegraphics[height=4cm]{chSPIE_2012_CA1/figs/ca1a_drawing}}
  \caption[Photo and design drawing of the IGRINS immersion grating]{Photo and design drawing of the immersion grating CA1a in the lab in August 2011.  The entrance face is on the right, with a light green color in the photo (color available in the digital manuscript), which is due to the AR coating.  The grating surface is on the top with microscopic grating lines perpendicular to the long edge of the grating.  In operation a 25 mm circular beam will be incident on the entrance face and will project into an ellipse on the grating surface as seen in the drawing.  The dispersed light will reemerge from the entrance face.  The units in the drawing are mm.  The parent substrate and grating geometry are pictured in Figures 1, 3, and 4 in Wang et al. 2010\cite{2010SPIE.7739E.146W}.  Those figures reveal how the CA1a trapezoid shape and curved rear edge derive from the parent substrate shape.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=0.9\textwidth]{chSPIE_2012_CA1/figs/CA1a_fig_scl2}
  \caption[Optical interferometry of the IGRINS immersion grating]{Optical interferometry of CA1a in reflection off the back surface before cutting and aluminization.  The color scales are in waves of surface error for 632 nm in reflection.  \emph{Left:} Interferogram measured in Littrow reflection at R3 over a 23.75 mm beam on the parent substrate CA1, in the vicinity where CA1a was later cut.  The colorbars show the vertical scale in waves of surface distortion at $\lambda = $ 632.8 nm.  These optical measurements illuminate the back of the grating facets, they were taken before aluminization and should be a good proxy for immersion performance at 2.15 $\mu$m. \emph{Center:} A fit to the large scale surface distortion using the first 200 Zernike polynomials in the Noll Sequence \cite{noll1976}.  \emph{Right:} The residual high spatial frequency surface error constructed from subtracting the fit from the measured surface error.}
  \label{fig:gram}
\end{figure}

@@

\begin{figure}
\begin{center}
    \includegraphics[width=1.0\textwidth]{chSPIE_2012_CA1/figs/GTA_cam_model_ref_tilt.jpg}
  \end{center}
  \caption[Schematic of the CROWBAR: Custom Robotic Order, Wavelength, and Blaze Angle Recorder]{\label{fig:GTAview} View of the monochromator, periscope, and swing arm-camera system with the beam path highlighted.  The beam exits the monochromator exit slit (8), where the optical chopper (9) is located.  The beam is collimated by a 1 inch post-slit lens (10).  The periscope system includes 3 mirrors (12, 13a, 13b), only two of which are active at any time.  In the reflective arm of interest to this report, we use mirrors (12) and (13b), with mirror 13a moved clear out of the beam path with a 90$^\circ$ flip mount.  The beam travels about 1 meter (off the image) to an adjustable iris in double pass (14, 16) sandwiching a mirror (15) tilted about 10$^\circ$ from the $z-y$ plane.  The beam travels along the vector terminating on the center of the immersion grating (17).  The immersion grating has its grooves vertical (parallel to the $z-$axis) so that the dispersion occurs in a the $x-y$ plane.  There are typically 3 or 4 orders diffracted $\pm20^\circ$ from the optical axis, for CA1 in our wavelength range of interest ($1.5-2.5 \; \mu$m).  The camera lens (18) and single pixel detector (19) are mounted on a swinging arm which rotates in the $x-y$ plane, with its center of rotation equal to the position of the immersion grating.  The angular range of motion of the swing arm is about +27 to -37$^\circ$ which is set by limit switches and the rigid mechanical structure, which supports the immersion grating and its concomitant fine adjust positioning hardware.  The cartoon arrows demonstrate our angular sign convention which is positive counter clockwise, with zero along the optic axis.  The grating normal is at about -70$^\circ$ with that convention.  The beam path in the monochromator is omitted for clarity.  The lock-in amplifier electronics are marked with number (20).}
\end{figure}

### 2015-04-08 chSPIE_2014_ebeam/chapter-2014-ebeam.tex
assign short figure captions to format nicely in the Table of Contents

@@

@@

\begin{figure}
   \subfloat[E12 Interferogram]{\label{fig:E12igram}\includegraphics[height=5cm]{chSPIE_2014_ebeam/figs/E12_fig_scl2.pdf}}
   \newline
  \subfloat[E09 Interferogram]{\label{fig:E09igram}\includegraphics[height=5cm]{chSPIE_2014_ebeam/figs/E09_fig_scl2.pdf}}
  \caption{Comparison of immersion grating surfaces on samples E09 and E12 measured with $\lambda = 632.8 $ nm interferometry.  These are both e-beam produced immersion grating surface prototypes.  The color scale is reported in fractions of waves of surface deviation.  The patterns on E09 and E12 are identical: $\sigma = $ 27.36 $\mu$m (about equal to 36.55 lines / mm), with a 9.96 $\mu$m groove top.  The groove top is not shadowed in these measurements which are taken in reflection in air, but we assume the groove tops have negligible impact on the measured interferometry.  The interferometry is performed with a 25 mm circular beam, which is projected over an 80 mm $\times$ 25 mm ellipse at the R3 echelle blaze angle, $\delta = 71.5 ^\circ$.  The left panel is the measured interferometry.  The middle panel is a decomposition into the first $\sim 80$ Zernike terms.  The right panel is the residual.  E09 was written on May 4, 2011, E12 was written September 1, 2011.  The only difference between the samples is that E12 was written with \emph{DRIFT} and \emph{CURRENT} check protocols with the JEOL e-beam writing software.  E09 was written without \emph{DRIFT} and \emph{CURRENT} check protocols.  The outcome is dramatic- E12 has $\sim 4$ times lower surface deformation than E09.  Note that the vertical color bars are on the same scale to ease visual comparison.}
  \label{fig:igrams}
\end{figure}

>>>>

\begin{landscape}

@@

\end{landscape}

@@

\begin{figure}
   \subfloat[E12 Interferogram]{\label{fig:E12igram}\includegraphics[height=5cm]{chSPIE_2014_ebeam/figs/E12_fig_scl2.pdf}}
   \newline
  \subfloat[E09 Interferogram]{\label{fig:E09igram}\includegraphics[height=5cm]{chSPIE_2014_ebeam/figs/E09_fig_scl2.pdf}}
  \caption[Interferometry reveals dramatic improvement in performance of e-beam produced immersion gratings]{Comparison of immersion grating surfaces on samples E09 and E12 measured with $\lambda = 632.8 $ nm interferometry.  These are both e-beam produced immersion grating surface prototypes.  The color scale is reported in fractions of waves of surface deviation.  The patterns on E09 and E12 are identical: $\sigma = $ 27.36 $\mu$m (about equal to 36.55 lines / mm), with a 9.96 $\mu$m groove top.  The groove top is not shadowed in these measurements which are taken in reflection in air, but we assume the groove tops have negligible impact on the measured interferometry.  The interferometry is performed with a 25 mm circular beam, which is projected over an 80 mm $\times$ 25 mm ellipse at the R3 echelle blaze angle, $\delta = 71.5 ^\circ$.  The left panel is the measured interferometry.  The middle panel is a decomposition into the first $\sim 80$ Zernike terms.  The right panel is the residual.  E09 was written on May 4, 2011, E12 was written September 1, 2011.  The only difference between the samples is that E12 was written with \emph{DRIFT} and \emph{CURRENT} check protocols with the JEOL e-beam writing software.  E09 was written without \emph{DRIFT} and \emph{CURRENT} check protocols.  The outcome is dramatic- E12 has $\sim 4$ times lower surface deformation than E09.  Note that the vertical color bars are on the same scale to ease visual comparison.}
  \label{fig:igrams}
\end{figure}

### 2015-04-08 chSiGaps/AO_bondedSi.tex
assign short figure captions to format nicely in the Table of Contents

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.60\columnwidth]{chSiGaps/figs/fpAbsorbfig_alt}
\end{center}
\caption{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\begin{center}
	\includegraphics[width=0.40\columnwidth]{chSiGaps/figs/etalon_trans.pdf}
\end{center}
\caption{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', defined as the Absolute transmission through a sample normalized by the absolute transmission through a gapless sample. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0-3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\`erot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{chSiGaps/figs/VS20fineGapCrop.pdf}
\end{center}
\caption{
\label{figVS20pattern}
Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\columnwidth]{chSiGaps/figs/VS2021_IR_image.pdf}
\end{center}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \label{figVG03_corner}}
    	 \newline
    \subfloat[][Measured spectrum and fit of VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f100.pdf} \label{figVG03_f100}}
	\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \label{figVG03p2_corner}}
    	\newline
    \subfloat[][Measured spectrum and fit of VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f045.pdf} \label{figVG03_f045}}
	\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Illustration of VG09-12 sample transport accessory measurement positions.]{\includegraphics[width=0.3\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf} \label{figVG0912_STA_illus}}
    \newline
    \subfloat[][Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\includegraphics[width=0.8\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf} \label{figVG0912}}
	\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf} \label{VG0912_0gap_corner}}
    \newline
    \subfloat[][Measured spectrum of VG09-12]{\includegraphics[width=0.65\textwidth]{chSiGaps/figs/VG0912_0gap.pdf} \label{VG0912_0gap}}
	\caption{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12-STA}}
\end{figure}

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.60\columnwidth]{chSiGaps/figs/fpAbsorbfig_alt}
\end{center}
\caption[Direct measurement of Si absorption as a function of wavelength]{Ratio of transmission of a 0.5 mm thick Si wafer to that of a 3.0 mm thick Si puck.  \label{figSiAbsorbfig} We detect Si absorption shortward of $\lambda$ = 1250 nm.  The individual measurements have correlated uncertainties attributable to lamp drift at the level of 0.2\%.  The random uncertainties are typically about 0.02\% per sample, though some wavelength regions (e.g. 1700-1900 nm) demonstrate much greater per sample uncertainties.  Absorption longward of 1250 nm (vertical dashed line) is negligible.}
\end{figure}

@@

\begin{figure}[!htbp]
\begin{center}
	\includegraphics[width=0.40\columnwidth]{chSiGaps/figs/etalon_trans.pdf}
\end{center}
\caption[Predicted effect size of transmission loss as a function of Si gap axial extent]{\label{figAbsoluteTrans}The family of normal-incidence curves for transmission as a function of wavelength for various gap sizes in bonded Si optics.  \emph{Top panel}: Absolute transmission through a Si substrate with no gap (top denim-blue solid curve), and small gaps of axial extent 20 nm (green dashed curve), 35 nm (red dash-dotted curve), and 60 nm (purple dotted curve).  The absolute transmission through Si depends on wavelength since the refractive index depends minutely on wavelength.  The curves assume that multiple reflections within the Si substrates add incoherently as discussed in detail in Appendix \ref{sec:Append-IMRTMM}.  \emph{Middle panel}: The ``Gap Transmission'', defined as the Absolute transmission through a sample normalized by the absolute transmission through a gapless sample. The gap sizes and colors are the same as in the top panel.  \emph{Bottom panel}: ``Gap Transmission'' for larger gaps, spanning 0-3500 nm.  The 3500 nm sized gap (cyan solid line), demonstrates characteristic Fabry-P\`erot etalon fringes.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\columnwidth]{chSiGaps/figs/VS20fineGapCrop.pdf}
\end{center}
\caption[Lab measurement of synthetic gap extent with precision optical profilometry]{\label{figVS20pattern} Veeco optical profiler surface plot and histogram for part VS20-21 in the fine pattern section.  The 100 mm diameter VS20-21 is comprised of two thick silicon wafers.  We patterned three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  The depth was $95 \pm 5\;$nm as indicated by the well-separated peaks in the Veeco profilometry histogram.  The fill factor for this and all mesh patterns was 50\%.  The purpose for these patterns was to have gaps of known axial extent against which we could test the optical metrology technique we describe in this article.}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\columnwidth]{chSiGaps/figs/VS2021_IR_image.pdf}
\end{center}
\caption[IR image of direct bonded Si wafers demonstrating interfacial gaps]{ \label{figVS2021_IR_image} IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_corner.pdf} \label{figVG03_corner}}
    	 \newline
    \subfloat[][Measured spectrum and fit of VG03 hole region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f100.pdf} \label{figVG03_f100}}
	\caption[MCMC corner plot and fitted spectrum for gap size parameters for a large 4 $\mu$m interfacial gap]{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths short-ward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.}
	\label{figVG03full} 
\end{figure}

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03p2_corner.pdf} \label{figVG03p2_corner}}
    	\newline
    \subfloat[][Measured spectrum and fit of VG03 petal region]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG03_f045.pdf} \label{figVG03_f045}}
	\caption[MCMC corner plot and fitted spectrum for gap size parameters when the gap fills only a small fraction of the measurement beam]{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. }
	\label{figVG03part}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Illustration of VG09-12 sample transport accessory measurement positions.]{\includegraphics[width=0.3\textwidth]{chSiGaps/figs/VG09_12_STA_illustration.pdf} \label{figVG0912_STA_illus}}
    \newline
    \subfloat[][Measured gap transmission spectra of VG09-12 on- and off- mesh ]{\includegraphics[width=0.8\textwidth]{chSiGaps/figs/VG0912_STA_scan_coarse.pdf} \label{figVG0912}}
	\caption[Spatially resolved near-IR spectroscopy of direct bonded Si optics- measurements consistent with prediction band]{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.}
	\label{figVG12}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \subfloat[][Fitted gap size $d$ and fill factor $f$ for VG09-12 off-mesh]{\includegraphics[width=0.5\textwidth]{chSiGaps/figs/VG0912_0gap_corner.pdf} \label{VG0912_0gap_corner}}
    \newline
    \subfloat[][Measured spectrum of VG09-12]{\includegraphics[width=0.65\textwidth]{chSiGaps/figs/VG0912_0gap.pdf} \label{VG0912_0gap}}
	\caption[We can constain interfacial gap axial extents to $<$14 nm]{Similar to Figure \ref{figVG03full} and \ref{figVG03part}, but for sample VG09-12 in the off-mesh region.  The measured spectrum in this region shows no appreciable deficit of transmission from a DSP reference sample.
	\label{figVG12-STA}}
\end{figure}
